MIP-GNN: A data-driven tool for guiding combinatorial solvers

### 2020-08-05 paper/main.tex
Startet paper.

\begin{algorithm}[H]\mbox{\hfill}
\\\textbf{Input:} System of linear equations $\vec{A} \vec{x} \geq \vec{b}$, $\varepsilon > 0$,  stepsize $\eta > 0$, scaling constant $\rho$, failure probability $\delta$. \\
\textbf{Output:} $\vec{\bar{x}}$ satisfying~\cref{epsfeas} or \texttt{non-feasible}
\begin{algorithmic}[1]
	\State Initialize constraint weights $w_i \leftarrow 1$ for $i$ in $[m]$ 
	\State Set $T$ to according~\cref{mwubound}
	\For{$t \text{ in } [T]$}
	\State Normalize weights $p_j \leftarrow \frac{w_j(t)}{\Phi(t)} $  for $i$ in $[m]$, where $\Phi(t) = \sum_{i \in [m]} w_i$
	\State Call oracle: $\vec{x}(t) \leftarrow \cO(\vec{p}\trans \vec{A} \vec{x} \geq \vec{p}\trans \vec{b})$ if $
	\vec{x}(t) = \emptyset$ \Return  \texttt{non-feasible}
	\State Compute error signal $\vec{m}$ with
	\begin{equation*}
		m_i \leftarrow \nicefrac{1}{\rho}\,(\vec{A}_i\trans \vec{x}(t) - b_i)   
	\end{equation*}
	\State Perform gradient descent  by $w_i(t+1) \leftarrow ( 1 -  \eta m_i) w_i(t) $ 
	\EndFor
	\State \Return $\vec{\bar{x}} \leftarrow \nicefrac{1}{T} \sum_{t \in [T]} \vec{x}(t) $
\end{algorithmic}
\caption{MWU for the LP feasibility problem.}
\label{alg:as}
\end{algorithm}

\begin{algorithm}[H]\mbox{\hfill}
	\\\textbf{Input:} $B(I)$, $\varepsilon > 0$,  stepsize $\eta > 0$, scaling constant $\rho$, failure probability $\delta$. \\
	\textbf{Output:} $\vec{\bar{x}}$ satisfying~\cref{epsfeas} or \texttt{non-feasible}
	\begin{algorithmic}[1]
		\State Initialize constraint weights $\vec{p}_j \leftarrow \nicefrac{1}{m}$ for each constraint node
		\State Set $T$ to according~\cref{mwubound}
		\For{$t \text{ in } [T]$}
		\State For each constraint node $\vec{c}_j$ send $\vec{p}_j$ to adjacent node variable 
		\Statex
		\State Update each variable node $\vec{v}_i$ based on output $\vec{x}_i$ of oracle using $\vec{p}$
		\Statex
		\State Send $\vec{x}_i$ to each adjacent constraint, compute error signal $\vec{m}_i$ for each constraint $\vec{c}_j$
		\begin{equation*}
		\vec{m}_j \leftarrow \nicefrac{1}{\rho}\,\Big(\sum_{i \in N(j)}\vec{A}_{ji}  \vec{x}_i \Big) - \vec{b}_j   
		\end{equation*}
		\State Perform gradient descent  by $\vec{w}_i(t+1) \leftarrow ( 1 -  \eta \vec{m}_i) \vec{w}_i(t) $ 
		\State Normalize weights $p_j \leftarrow \frac{w_j(t)}{\Phi(t)}$ for each constraint node, where $\Phi(t) = \sum_{i \in [m]} w_i$

		\EndFor
		\State \Return $\vec{\bar{x}} \leftarrow \nicefrac{1}{T} \sum_{t \in [T]} \vec{x}(t) $
	\end{algorithmic}
	\caption{MWU (Message Passing version) for the LP feasibility problem.}
	\label{alg:as}
\end{algorithm}

@@

\begin{algorithm}[H]\mbox{\hfill}
	\\\textbf{Input:}  Training set $\cS$, $\varepsilon > 0$, number of rounds $T$, stepsize $\eta > 0$, scaling constant $\rho$.  \\
	\textbf{Output:} A trained model $f_{\boldsymbol{\theta}} \colon \cI \to [0,1]^n$ 
	\begin{algorithmic}[1]
		\State Initialize $\vec{v}_i^{(0)}$, $\vec{c}_i^{(0)}$, and $\boldsymbol{\theta}$
		\State Set weights $\vec{w}_j^{(0)} \leftarrow 1$, $\vec{p}_j^{(0)} \leftarrow \nicefrac{1}{m}$ for $j$ in $[m]$
		\Statex
		\For{$e \text{ in } [E]$}
		\State \cm{Make p a parameter?}
		\State Sample $I = (\vec{c}, \vec{A}, \vec{b})$ with bias  $\vec{\bar{b}}$ uniformly and at random from $\cS$ \cm{define Ib}
		\For{$t \text{ in } [T]$}
		\State $\vec{v}_i^{(t)} \leftarrow \mathbf{f}^{(t)}_{\text{V}} \hspace{-2pt} \left( \left\{ \hspace{-5pt} \left\{ \left( \vec{v}^{(t-1)}_i, \vec{c}_j, \vec{A}_{ij}, \vec{p}_j \right)\hspace{-3pt} \colon j \in N(\vec{v}_i) \right\} \hspace{-5pt} \right\} \right)\quad$		 $\vec{x}_i^{(t)} \leftarrow \mathbf{f}^{(t)}_{\text{V}}   \hspace{-2pt} \left(\vec{v}_i^{(t-1)} \right)$ %\cm{Oracle?}
		%\Statex
		\State $\vec{c}_j^{\hspace{1pt}(t)} \leftarrow \mathbf{f}^{(t)}_{\text{C}} \hspace{-2pt} \left( \left\{ \hspace{-5pt} \left\{ \left( \vec{c}^{(t-1)}_j, \vec{v}_i, \vec{x}_i, \vec{A}_{ij}, \vec{b}_j \right)\hspace{-3pt} \colon i \in N(\vec{c}_j) \right\} \hspace{-5pt} \right\} \right)$
		\State $\vec{e}_j^{(t)} \leftarrow \nicefrac{1}{\rho}\! \sum_{i \in N(j)} \vec{A}_{ji} \vec{x}_i^{(t)} - \vec{b}_j$
		%\Statex
		\State $\vec{w}_j^{(t)} \leftarrow ( 1 -  \eta \vec{e}_j) \vec{w}_j^{(t)} $ 
		\State $\vec{p}_j \leftarrow \frac{w_j^{(t)}}{\Phi(t)} $, where $\Phi(t) = \sum_{j \in [m]} \vec{w}^{(t)}_j$
		\EndFor
		\State g
		\State $\vec{\bar{x}} \leftarrow \nicefrac{1}{T} \sum_{t \in [T]} \vec{x}(t) $
		\State $L \leftarrow L + \ell(\vec{\bar{x}}, \vec{\bar b})$ 
		\State Gradient descent on L
		\EndFor
		\State \Return $\boldsymbol{\theta}$

	\end{algorithmic}
	\caption{Data-driven MWU for variable bias prediction.}
	\label{alg:as2}
\end{algorithm}
\cm{overloading of c}

\subsection{Unsupervised setting}

@@

discuss limitation of GNNs approaches, unsupervised approaches

>>>>

\begin{algorithm}[H]\mbox{\hfill}
\\\textbf{Input:} System of linear equations $\vec{A} \vec{x} \geq \vec{b}$, $\varepsilon > 0$,  stepsize $\eta > 0$, scaling constant $\rho$. \\
\textbf{Output:} $\vec{\bar{x}}$ satisfying~\cref{epsfeas} or \texttt{non-feasible}
\begin{algorithmic}[1]
	\State Initialize constraint weights $\vec{w}_i \leftarrow 1$ for $i$ in $[m]$ 
	\State Initialize probabilities $\vec{p}_j \leftarrow \nicefrac{1}{m}$ for $i$ in $[m]$ 
	\State Set $T$ to according~\cref{mwubound}
	\For{$t \text{ in } [T]$}

	\State Call oracle: $\vec{x} \leftarrow \cO(\vec{p}\trans \vec{A} \vec{x} \geq \vec{p}\trans \vec{b})$, \textbf{if} $
	\vec{x} = \emptyset$ \Return  \texttt{non-feasible}
	\State Compute error signal $\vec{e}$, where
	\begin{equation*}
		\vec{e}_j \leftarrow \nicefrac{1}{\rho}\,(\vec{A}_j\trans \vec{x}(t) - \vec{b}_j)   
	\end{equation*}
	\State Perform gradient descent by $\vec{w}_i \leftarrow (1 - \eta \vec{e}_i) \vec{w}_i$ 
	\State Normalize weights $\vec{p}_j \leftarrow \nicefrac{\vec{w}_j}{\Phi} $  for $i$ in $[m]$, where $\Phi = \sum_{i \in [m]} \vec{w}_i$
	\State Update solution $\vec{\bar{x}} \leftarrow \vec{\bar{x}} + \vec{x}$
	\EndFor
	\State \Return Average over solution $ \nicefrac{\vec{\bar{x}}}{T} $
\end{algorithmic}
\caption{MWU for the LP feasibility problem.}
\label{alg:as}
\end{algorithm}

\begin{algorithm}[H]\mbox{\hfill}
	\\\textbf{Input:} Biparite constraint graph $B(I)$, $\varepsilon > 0$,  stepsize $\eta > 0$, scaling constant $\rho$. \\
	\textbf{Output:} $\vec{\bar{x}}$ satisfying~\cref{epsfeas} or \texttt{non-feasible}
	\begin{algorithmic}[1]
		\State Initialize weights $\vec{w}_j \leftarrow 1$ for each constraint node
		\State Initialize probabilities $\vec{p}_j \leftarrow \nicefrac{1}{m}$ for each constraint node
		\State Set $T$ to according~\cref{mwubound}
		\For{$t \text{ in } [T]$}
		\State For each constraint node $\vec{c}_j$ send $\vec{p}_j$ to adjacent node variable 
		\State Update each variable node $\vec{v}_i$ based on output $\vec{x}_i$ of oracle using $\vec{p}$
		\State Send $\vec{v}_i$ to each adjacent constraint, compute error signal $\vec{e}_i$ for each constraint $\vec{c}_j$
		\begin{equation*}
		\vec{e}_j \leftarrow \nicefrac{1}{\rho}\,\Big(\sum_{i \in N(j)} \vec{A}_{ji}  \vec{v}_i \Big) - \vec{b}_j   
		\end{equation*}
		\State Perform gradient descent by $\vec{w}_i \leftarrow (1 - \eta \vec{e}_i) \vec{w}_i$ 
		\State Normalize weights $\vec{p}_j \leftarrow \nicefrac{\vec{w}_j}{\Phi} $  for $i$ in $[m]$, where $\Phi = \sum_{i \in [m]} \vec{w}_i$
		\State Update solution $\vec{\bar{x}} \leftarrow \vec{\bar{x}} + \vec{x}$
		\EndFor
		\State \Return Average over solution $ \nicefrac{\vec{\bar{x}}}{T}$
	\end{algorithmic}
	\caption{MWU (Message passing version) for the LP feasibility problem.}
	\label{alg:as}
\end{algorithm}

@@

\begin{algorithm}[H]\mbox{\hfill}
	\\\textbf{Input:}  Training set $\cS$, $\varepsilon > 0$, number of rounds $T$, stepsize $\eta > 0$, scaling constant $\rho$.  \\
	\textbf{Output:} A trained model $f_{\boldsymbol{\theta}} \colon \cI \to [0,1]^n$ 
	\begin{algorithmic}[1]
		\State Initialize $\vec{v}_i^{(0)}$, $\vec{c}_i^{(0)}$, and $\boldsymbol{\theta}$
		\State Set weights $\vec{w}_j^{(0)} \leftarrow 1$, $\vec{p}_j^{(0)} \leftarrow \nicefrac{1}{m}$ for $j$ in $[m]$
		\Statex
		\For{$e \text{ in } [E]$}
		\State \cm{Make p a parameter?}
		\State Sample $I = (\vec{c}, \vec{A}, \vec{b})$ with bias  $\vec{\bar{b}}$ uniformly and at random from $\cS$ \cm{define Ib}
		\For{$t \text{ in } [T]$}
		\State $\vec{v}_i^{(t)} \leftarrow \mathbf{f}^{(t)}_{\text{V}} \hspace{-2pt} \left( \left\{ \hspace{-5pt} \left\{ \left( \vec{v}^{(t-1)}_i, \vec{c}_j, \vec{A}_{ij}, \vec{p}_j \right)\hspace{-3pt} \colon j \in N(\vec{v}_i) \right\} \hspace{-5pt} \right\} \right)\quad$		 $\vec{x}_i^{(t)} \leftarrow \mathbf{f}^{(t)}_{\text{V}}   \hspace{-2pt} \left(\vec{v}_i^{(t-1)} \right)$ %\cm{Oracle?}
		%\Statex
		\State $\vec{c}_j^{\hspace{1pt}(t)} \leftarrow \mathbf{f}^{(t)}_{\text{C}} \hspace{-2pt} \left( \left\{ \hspace{-5pt} \left\{ \left( \vec{c}^{(t-1)}_j, \vec{v}_i, \vec{x}_i, \vec{A}_{ij}, \vec{b}_j \right)\hspace{-3pt} \colon i \in N(\vec{c}_j) \right\} \hspace{-5pt} \right\} \right)$
		\State $\vec{e}_j^{(t)} \leftarrow \nicefrac{1}{\rho}\! \sum_{i \in N(j)} \vec{A}_{ji} \vec{x}_i^{(t)} - \vec{b}_j$
		%\Statex
		\State $\vec{w}_j^{(t)} \leftarrow ( 1 -  \eta \vec{e}_j) \vec{w}_j^{(t)} $ 
		\State $\vec{p}_j \leftarrow \frac{w_j^{(t)}}{\Phi(t)} $, where $\Phi(t) = \sum_{j \in [m]} \vec{w}^{(t)}_j$
		\EndFor
		\State g
		\State $\vec{\bar{x}} \leftarrow \nicefrac{1}{T} \sum_{t \in [T]} \vec{x}(t) $
		\State $L \leftarrow L + \ell(\vec{\bar{x}}, \vec{\bar b})$ 
		\State Gradient descent on $L$
		\EndFor
		\State \Return $\boldsymbol{\theta}$

	\end{algorithmic}
	\caption{Data-driven MWU for variable bias prediction.}
	\label{alg:as2}
\end{algorithm}
\cm{overloading of c}
\cm{how to incoperate data information}
\subsection{Unsupervised setting}

@@

discuss limitation of GNNs approaches (bipartite GNN), unsupervised approaches
